Hierarchical Principal Manifold Estimation

### 2023-08-11 paper/main.tex
bibliography test

\usepackage[
backend=biber,
style=authoryear
]{biblatex}

@@

As mentioned previously, this proposed additive spline model structure has several benefits.

>>>>

\usepackage[
  backend=biber,
  style=numeric
]{biblatex}

@@

As mentioned previously, this proposed additive spline model structure has several benefits. First, it maintains interpretability at each level of the model. It is possible to visually inspect the embedding maps of the population and each group and individual to better understand how they interact. Additionally, basing our handling of the data's hierarchical structure on a statistical model allows us to assess statistical properties of the estimated manifold, where less statistically principled approaches make this option difficult.
